### 2018-12-04 tex/appendix.tex
Edited the appendix section for Potts model.

\begin{equation}
    \sum_{A \in {\mathcal M}} \exp(-s(A)) = \prod_{a = 1}^{N} \sum_{i = 1}^L \exp(-s_{ai})
    %%\label{eq:ind}
\end{equation}

Let $t$ be the number of variables, $V^t$ be the corresponding ground set and ${\mathcal M}^t$ be the sets corresponding to valid labelings. Equation \eqref{eq:ind} clearly holds for $t = 1$.

@@

\begin{align}
    \sum_{A^{N + 1} \in {\mathcal M}^{N + 1}} \exp(-s(A^{N + 1})) &=  \sum_{i = 1}^L \sum_{A^N \in {\mathcal M}^{N}} \exp(-s(A^N) - s_{N+1, i}) \nonumber \\
                                                                  &= \sum_{i = 1}^L \exp(-s_{N+1, i}) \sum_{A^N \in {\mathcal M}^{N}} \exp(-s(A^N) ) \nonumber \\
                                                                  &= \sum_{i = 1}^L \exp(-s_{N+1, i}) \prod_{a = 1}^{N} \sum_{i = 1}^L \exp(-s_{ai}) \nonumber \\
                                                                  &= \prod_{a = 1}^{N + 1} \sum_{i = 1}^L \exp(-s_{ai})
\end{align}

{\lemma Given any submodular extension $F(.)$ of a Potts energy function $E(.)$, its Lovasz extension $f(.)$ defines an LP relaxation of the MAP problem for $E(.)$ as 
\begin{align}
    \min_{{\bf y} \in \Delta} f({\bf y}).
\end{align}
%\label{lemma:lovasz_lp}}
\begin{proof}
    By definition of a submodular extension and the Lovasz extension, $E({\bf x}) = F(A_{\bf x}) = f(1_{A_{\bf x}})$ for all valid labelings ${\bf x}$. Also, from property 1, $f({\bf y})$ is maximum of linear functions. Hence, $f({\bf y})$ is a piecewise linear relaxation of $E({\bf x})$.

@@

{\proposition In the limit $T \to 0$, the following problem for Potts energies 
\begin{equation}
    \min_{{\bf s} \in EP(F)} \quad g_T ({\bf s}) = \sum_{a = 1}^{N} T \cdot \log \sum_{i = 1}^L \exp(-\frac{s_{ai}}{T}).
%\label{eq:potts_temp}
\end{equation}

becomes
\begin{align}
    - \min_{{\bf y} \in \Delta} f({\bf y}) 
\end{align}
%\label{proposition:potts_equiv}}

{\proposition The objective function $E({\bf y})$ of the LP relaxation (P-LP) is the Lovasz extension of $F_{Potts}(A) = \sum_{i = 1}^L F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} \frac{w_{ab}}{2} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
%\label{proposition:a-potts_optimal}}

\begin{proof}
Since $F_{Potts}$ is sum of Ising models $F_i$, we first focus on a particular label $i$ and then generalize. Consider a graph with only two variables $X_a$ and $X_b$ with an edge between them. The ground set in this case is $\{v_{ai}, v_{bi}\}$. Let the corresponding relaxed indicator variables be ${\bf y} = \{y_{aj}, y_{bj}\}$, such that $y_{ai}, y_{bi} \in [0, 1]$ and assume $y_{ai} > y_{bi}$. The Lovasz extension in this case is:

\begin{align}
f({\bf y}) &= y_{ai} \cdot [F_i(\{v_{ai}\}) - F_i(\{\})] + y_{bi} \cdot [F_i(\{v_{ai}, v_{bi}\}) - F_i(\{v_{ai}\})] \nonumber \\
&= y_{ai} \cdot [\left(\phi_{a}\left(j\right) + \frac{w_{ab}}{2}\right) - 0] + y_{bi} \cdot [\left(\phi_{a}\left(j\right) + \phi_{b}\left(j\right)\right) - \left(\phi_{a}\left(j\right) + \frac{w_{ab}}{2}\right)] \nonumber \\
&=  \phi_{a}\left(j\right) \cdot y_{ai} + \phi_{b}\left(j\right) \cdot y_{bi} + \frac{w_{ab}}{2} \cdot \left(y_{ai} - y_{bi}\right)
\end{align}

In general for both orderings of $y_{ab}$ and $y_{bi}$, we can write
%
\begin{equation}
f({\bf y}) = \phi_{a}(j) \cdot y_{ai} + \phi_{b}(j) \cdot y_{bi} + \frac{w_{ab}}{2} \cdot |y_{ai} - y_{bi}|
%\label{eq:a-lovasz_ising}
\end{equation}
%
Extending the Lovasz extension of equation \eqref{eq:a-lovasz_ising} to all variables and all labels gives us $E({\bf y})$ in (P-LP). 
\end{proof}

@@

{\proposition The objective function $\widetilde{E}({\bf z})$ of (T-LP-FULL) is the Lovasz extension of $F_{r-\textrm{HST}}(A) = \sum_{i = 1}^M F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi'_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} {w_{ab}} \cdot l_{T_i} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
%\label{proposition:rhst_optimal}}
\begin{proof}
    We observe that $F_{r-\textrm{HST}}$ is of exactly the same form as $F_{Potts}$, except that the Ising models $F_i$ are defined over not just labels, but meta-labels as well. Using the same logic as in the proof of proposition \ref{proposition:a-potts_optimal}, each $F_i$ is the Lovasz extension of 
        \begin{equation}
            \widetilde{E}_i({\bf z}) = \left( \sum_{a \in {\mathcal X}} \phi_a'(i) \cdot z_{ai} + \sum_{(a, b) \in {\mathcal N}} w_{ab} \cdot l_{T_i} \cdot |z_{ai} - z_{bi}| \right)
        \end{equation}
    and the results follows. 
\end{proof}

\section{Additional Experiment Results}

@@

Figure \ref{fig:stereo_hier} shows the solutions obtained by picking the label with maximum marginal probability for each variable for mean-field and for our algorithm. We also report the time and energy values of the solution for both methods. Though we are not performing MAP estimation, energy values give us a quantitative indication of the quality of solutions. We observe that our algorithm results in more natural looking stereo matching results. However, mean-field gives lower energy value solutions and runs faster than our method for each instance.
\clearpage

>>>>

\begin{equation}
    \sum_{A \in {\mathcal M}} \exp(-s(A)) = \prod_{a = 1}^{N} \sum_{i = 1}^L \exp(-s_{ai})
    \label{eq:ind}
\end{equation}

\begin{proof}
Let $t$ be the number of variables, $V^t$ be the corresponding ground set and ${\mathcal M}^t$ be the sets corresponding to valid labelings. Equation \eqref{eq:ind} clearly holds for $t = 1$.

@@

\begin{align}
    \sum_{A^{N + 1} \in {\mathcal M}^{N + 1}} \exp(-s(A^{N + 1})) &=  \sum_{i = 1}^L \sum_{A^N \in {\mathcal M}^{N}} \exp(-s(A^N) - s_{N+1, i}) \nonumber \\
                                                                  &= \sum_{i = 1}^L \exp(-s_{N+1, i}) \sum_{A^N \in {\mathcal M}^{N}} \exp(-s(A^N) ) \nonumber \\
                                                                  &= \sum_{i = 1}^L \exp(-s_{N+1, i}) \prod_{a = 1}^{N} \sum_{i = 1}^L \exp(-s_{ai}) \nonumber \\
                                                                  &= \prod_{a = 1}^{N + 1} \sum_{i = 1}^L \exp(-s_{ai})
\end{align}
\end{proof}
{\lemma Given any submodular extension $F(.)$ of a Potts energy function $E(.)$, its Lovasz extension $f(.)$ defines an LP relaxation of the MAP problem for $E(.)$ as 
\begin{align}
    \min_{{\bf y} \in \Delta} f({\bf y}).
\end{align}
%\label{lemma:lovasz_lp}}
\begin{proof}
    By definition of a submodular extension and the Lovasz extension, $E({\bf x}) = F(A_{\bf x}) = f(1_{A_{\bf x}})$ for all valid labelings ${\bf x}$. Also, from property 1, $f({\bf y})$ is maximum of linear functions. Hence, $f({\bf y})$ is a piecewise linear relaxation of $E({\bf x})$.

@@

@@

{\proposition The objective function $\widetilde{E}({\bf z})$ of (T-LP-FULL) is the Lovasz extension of $F_{r-\textrm{HST}}(A) = \sum_{i = 1}^M F_i(A)$, where
\begin{align}
    F_i(A) &= \sum_a \phi'_{a}(i) [|A \cap \{v_{ai}\}| = 1] + \nonumber \\
           &\sum_{(a, b) \in {\mathcal N}} {w_{ab}} \cdot l_{T_i} \cdot [|A \cap \{v_{ai}, v_{bi}\}| = 1]
\end{align}
%\label{proposition:rhst_optimal}}
\begin{proof}
    We observe that $F_{r-\textrm{HST}}$ is of exactly the same form as $F_{Potts}$, except that the Ising models $F_i$ are defined over not just labels, but meta-labels as well. Using the same logic as in the proof of proposition \ref{proposition:a-potts_optimal}, each $F_i$ is the Lovasz extension of 
        \begin{equation}
            \widetilde{E}_i({\bf z}) = \left( \sum_{a \in {\mathcal X}} \phi_a'(i) \cdot z_{ai} + \sum_{(a, b) \in {\mathcal N}} w_{ab} \cdot l_{T_i} \cdot |z_{ai} - z_{bi}| \right)
        \end{equation}
    and the results follows. 
\end{proof}
\iffalse
\section{Additional Experiment Results}

@@

Figure \ref{fig:stereo_hier} shows the solutions obtained by picking the label with maximum marginal probability for each variable for mean-field and for our algorithm. We also report the time and energy values of the solution for both methods. Though we are not performing MAP estimation, energy values give us a quantitative indication of the quality of solutions. We observe that our algorithm results in more natural looking stereo matching results. However, mean-field gives lower energy value solutions and runs faster than our method for each instance.
\fi
\clearpage
